Radial Velocity Upper Limits on Planets around Radio Exoplanet Candidates GJ~1151 and GJ~412A

### 2019-02-28 paper/ms.tex
mass limits

Rather than explicitly searching for radio emission from known exoplanet hosts, \citet{Callingham_2019} cross-matched sources identified by the LOFAR Two-meter Sky Survey (LoTSS) with nearby stellar sources found by \gaia, finding the great majority of matches to be chance associations. But by restricting the survey to variable and circularly-polarized emission, the rate of chance associations with background radio galaxies is dramatically reduced. Based on this restricted cross-match, Vedantham et al. (submitted) and Callingham et al. (submitted) have detected the M~dwarfs GJ~1151 and GJ~412A respectively at low radio frequencies with LOFAR, finding a high degree of circular polarization consistent with a possible star-planet magnetic interaction analogous to a scaled-up Jupiter and Io.

@@

In their publication, \citet{hires} did not claim a detection of any planet-like Keplerian signal from GJ~412A, though they did identify a 28~day period in the S~indices of activity. We do not re-extract RVs from these data, censoring only two outliers with $\text{RV}>10\,\text{m/s}$.

>>>>

Rather than explicitly searching for radio emission from known exoplanet hosts, \citet{Callingham_2019} cross-matched sources identified by the LOFAR Two-meter Sky Survey (LoTSS) with nearby stellar sources found by \gaia, finding the great majority of matches to be chance associations. But by restricting the survey to variable and circularly-polarized emission, the rate of chance associations with background radio galaxies is dramatically reduced. Based on this restricted cross-match, Vedantham et al. (submitted) and Callingham et al. (submitted) have detected the red dwarfs GJ~1151 and GJ~412A \citep[M1.0:][]{} respectively at low radio frequencies with LOFAR, finding a high degree of circular polarization consistent with a possible star-planet magnetic interaction analogous to a scaled-up Jupiter and Io.

@@

In their publication, \citet{hires} did not claim a detection of any planet-like Keplerian signal from GJ~412A, though they did identify a 28~day period in the S~indices of activity. We re-analyze their data to search for possible planet signals, but do not re-extract RVs, censoring only two outliers with $\text{RV}>10\,\text{m/s}$. Unlike the months of observations of GJ~1151, these data consist of 164 epochs over a sixteen-year period with very irregular sampling, though half of these epochs come in pairs separated by one day, and a quarter in triplets separated by one day, so that these data critically-sample 2~day periods.

We put $99^{\text{th}}$-percentile upper limits on the mass of any companion to GJ~412A and GJ~1151 respectively at 3.5~\msun and 5.1~\msun respectively.
